My title

### 2024-03-14 paper/paper.qmd
revise

deaths_data <- read.csv(here("data/analysis_data/cleaned_file.csv"))
air_quality_data <- read.csv(here("data/analysis_data/cleaned_air_data.csv"))
data <- read.csv(here("data/analysis_data/cleaned_chart_data.csv"))
data_peak <- read.csv(here("data/analysis_data/cleaned_peak_data.csv"))
```

@@

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))

@@

causes_model <-
  readRDS(file = here::here("models/causes_model.rds"))

p_average_model <-
  readRDS(file = here::here("models/p_average_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  #statistic = "mad",
  fmt = 2
)

modelsummary::modelsummary(
  list(
    "First model" = poisson_model
  ),
  #statistic = "mad",
  fmt = 2
)

modelsummary::modelsummary(
  list(
    "First model" = causes_model
  ),
  #statistic = "mad",
  fmt = 2
)

modelsummary::modelsummary(
  list(
    "First model" = p_average_model
  ),
  #statistic = "mad",
  fmt = 2
)
```

# Discussion

@@

pp_check(p_average_model) +
  theme(legend.position = "bottom")

# Create the posterior predictive check plot with the specified theme
pp_plot <- pp_check(p_average_model, theme = theme_classic()) +
  theme(legend.position = "bottom")

# Create the posterior vs prior plot with the specified theme
posterior_plot <- posterior_vs_prior(p_average_model, theme = theme_minimal()) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

>>>>

deaths_data <- read.csv(here("data/analysis_data/cleaned_file.csv"))
air_quality_data <- read.csv(here("data/analysis_data/cleaned_air_data.csv"))
data <- read.csv(here("data/analysis_data/cleaned_chart_data.csv"))
data_peak <- read.csv(here("data/analysis_data/cleaned_peak_data.csv"))
data_lung <- read.csv(here("data/analysis_data/merged_data.csv"))
data_heart <- read.csv(here("data/analysis_data/merged_heart_data.csv"))
```

@@

# Plot the regression graph for all lungs causes
ggplot(data_lung, aes(x = provincial_average, y = total_deaths)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +  # Add linear regression line without confidence interval
  labs(x = "Provincial Average", y = "Total Deaths", title = "Regression Lung") +
  theme_minimal()

# Plot the regression graph for all heart causes
ggplot(data, aes(x = provincial_average, y = total_deaths)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +  # Add linear regression line without confidence interval
  labs(x = "Provincial Average", y = "Total Deaths", title = "Regression Heart") +
  theme_minimal()

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
# 
# library(rstanarm)
# 
# first_model <-
#   readRDS(file = here::here("models/first_model.rds"))
# 
# poisson_model <-
#   readRDS(file = here::here("models/poisson_model.rds"))
# 
# causes_model <-
#   readRDS(file = here::here("models/causes_model.rds"))
# 
# p_average_model <-
#   readRDS(file = here::here("models/p_average_model.rds"))
#

library(rstanarm)
library(here)
library(ggplot2)
library(modelsummary)

# Assuming you've already read your models as before
neg_binom_model <- readRDS(file = here::here("models/neg_binom_model.rds"))
stan_neg_binom_model <- readRDS(file = here::here("models/stan_neg_binom_model.rds"))
stan_poisson_model <-readRDS(file = here::here("models/stan_poisson_model.rds"))
peak_neg_binom_model <- readRDS(file = here::here("models/peak_neg_binom_model.rds"))
peak_poisson_model <-readRDS(file = here::here("models/peak_poisson_model.rds"))
first_model <-
  readRDS(file = here::here("models/first_model.rds"))

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false
library(modelsummary)
# modelsummary::modelsummary(
#   list(
#     "First model" = first_model
#   ),
#   #statistic = "mad",
#   fmt = 2
# )
# 
# modelsummary::modelsummary(
#   list(
#     "First model" = poisson_model
#   ),
#   #statistic = "mad",
#   fmt = 2
# )
# 
# modelsummary::modelsummary(
#   list(
#     "First model" = causes_model
#   ),
#   #statistic = "mad",
#   fmt = 2
# )
# 
# modelsummary::modelsummary(
#   list(
#     "First model" = p_average_model
#   ),
#   #statistic = "mad",
#   fmt = 2
# )
#

if (!requireNamespace("modelsummary", quietly = TRUE)) {
  install.packages("modelsummary")
}
library(modelsummary)

if (!requireNamespace("broom.mixed", quietly = TRUE)) {
  install.packages("broom.mixed")
}

library(broom.mixed)

coef_short_names <- 
  c("causeAll other forms of chronic ischemic heart disease" = "Ischemic Heart Disease",
    "causeMalignant neoplasms of trachea, bronchus and lung" = "Trachea/Bronchus/Lung Cancer",
    "causeOrganic dementia" = "Organic Dementia",
    "causeOther chronic obstructive pulmonary disease" = "COPD"
  )

# Summarize the models
modelsummary(
  list(
    "Poisson" = poisson_model,
    "Negative binomial" = first_model
  ),
  coef_map = coef_short_names,
  estimate_function = function(model) {
    broom.mixed::tidy(model, parameters = "all", conf.int = TRUE)
  }
)

```
# Discussion

@@

pp_check(first_model) +
  theme(legend.position = "bottom")

pp_check(poisson_model) +
  theme(legend.position = "bottom")

pp_stan_neg_binom_model <- pp_check(stan_neg_binom_model)
pp_stan_neg_binom_model + theme(legend.position = "bottom")

pp_stan_poisson_model <- pp_check(stan_poisson_model)
pp_stan_poisson_model + theme(legend.position = "bottom")

pp_check(peak_poisson_model) +
  theme(legend.position = "bottom")

pp_stan_neg_binom_model <- pp_check(peak_poisson_model)
pp_stan_neg_binom_model + theme(legend.position = "bottom")

pp_check(peak_neg_binom_model) +
  theme(legend.position = "bottom")

pp_stan_neg_binom_model <- pp_check(peak_neg_binom_model)
pp_stan_neg_binom_model + theme(legend.position = "bottom")
